Modelling demography in the TREE package

### 2015-05-14 tree_demography.Rmd
Section on metapopulation and fitness

Let us now consider how we can estimate the fitness of a rare individual with trats $x^\prime$ growing in the environment of a resident community with traits $x$. We will focus on the phenotypic components of fitness -- i.e. the consequences of a given set of traits for growth, fecundity and mortality -- only, taking into account the non-linear effects of competition on individual success, but ignoring the underlying genetic basis for the trait determination. We also adhere to the standard conventions in such analyses in assuming that the mutant is sufficiently rare to have a negligible effect on the environment where it is growing.

>>>>

Let us now consider how we can estimate the fitness of a rare individual with traits $x^\prime$ growing in the environment of a resident community with traits $x$. We will focus on the phenotypic components of fitness -- i.e. the consequences of a given set of traits for growth, fecundity and mortality -- only, taking into account the non-linear effects of competition on individual success, but ignoring the underlying genetic basis for the trait determination. We also adhere to the standard conventions in such analyses in assuming that the mutant is sufficiently rare to have a negligible effect on the environment where it is growing.
